---
title: "Calendar"
author: Giuliano Colosimo
date: "2024-04-04"
date-modified: "2024-04-04"
bibliography: /Users/giulianocolosimo/Library/CloudStorage/ProtonDrive-giuliano.colosimo@protonmail.com/manuscripts/literature/bibtex/comprehensive_database.bib
csl: /Users/giulianocolosimo/Library/CloudStorage/ProtonDrive-giuliano.colosimo@protonmail.com/manuscripts/literature/bibtex/apa_5th_edition.csl
citation_package: biblatex
citecolor: "red"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
x <- c("calendR",
       "ggthemes",
       "lubridate",
       "scales",
       "tidyverse",
       "XML", "xml2")
lapply(x, require, character.only = T)
rm(x)
```

- Below you will find a temptative schedule for the rest of the semester. When you see your name written in one of the class date that means that it is your turn to present the manuscript that has been assigned to you. Manuscript and dates have been assigned in a random way. Please, if you already know that you will not be present on the date that has been assigned to you let me know in time so that I can arrange a schedule change.


```{r echo=FALSE}
#| out-width: 100%

dates <- seq(as.Date("2024-04-01"), as.Date("2024-04-30"), by = "1 day")
events <- ifelse(format(dates, "%w") %in% c(6, 0), "Weekend", NA)
events[c(4, 9, 11, 16, 18, 23)] <- "Class"
events[30] <- "Exam"
calendR(month = 4,
        start = "M",
        special.days = events,
        special.col = c("green", "red", "gray"),
        legend.pos = "bottom",
        pdf = F, 
        day.size = 3, 
        weeknames.size = 4, 
        title = "April",
        subtitle="2024",
        text = c("Falvo", "D'Alessandro", "Piroli"),
        text.pos = c(16, 18, 23),        
        text.size = 2.5,              
        text.col = "black")
```



```{r echo=FALSE}
#| out-width: 100%

dates <- seq(as.Date("2024-05-01"), as.Date("2024-05-31"), by = "1 day")
events <- ifelse(format(dates, "%w") %in% c(6, 0), "Weekend", NA)
events[c(2, 7, 9, 16, 21, 23, 28, 30)] <- "Class"
calendR(month = 5,
        start = "M",
        special.days = events,
        special.col = c("green", "gray"),
        legend.pos = "bottom",
        pdf = F, 
        day.size = 3, 
        weeknames.size = 4, 
        title = "May",
        subtitle="2024",
        text = c("Troncone", "Garcia", "Spera", "Toti", "Palmeri", "GdF", "Bonventre\nCacciuni\nSeminar"),
        text.pos = c(2, 7, 9, 16, 21, 28, 30),        
        text.size = 2.5,              
        text.col = "black")
```


```{r echo=FALSE}
#| out-width: 100%

dates <- seq(as.Date("2024-06-01"), as.Date("2024-06-30"), by = "1 day")
events <- ifelse(format(dates, "%w") %in% c(6, 0), "Weekend", NA)
events[c(4,6,11)] <- "Class"
events[13] <- "Exam"
calendR(month = 6,
        start = "M",
        special.days = events,
        special.col = c("green", "red", "gray"),
        legend.pos = "bottom",
        pdf = F, 
        day.size = 3, 
        weeknames.size = 4, 
        title = "June",
        subtitle="2024",
#        text = c(),
#        text.pos = c(2, 7, 9, 16, 21, 30),        
        text.size = 2.5,              
        text.col = "black")

```



- The table below has the student's name associated with the assigned paper


| Student      | Title            |
|--------------|------------------|
| FALVO        | [Developing gene drive technologies to eradicate invasive rodents from islands](https://drive.proton.me/urls/9WVQGE6J5M#GEndO0gEvVJq)      |
| D'ALESSANDRO | [Population genetic analysis of the recently rediscovered hula painted frog (*Latonia nigriventer*) reveals high genetic diversity and low inbreeding](https://drive.proton.me/urls/HQMV65ETB0#vB21xDrPrAXN) |
| PIROLI       | [First evidence of recruitment in critically endangered Galapagos pink iguanas](https://drive.proton.me/urls/TD1F4DDC70#hzwxC3gFnM51)  |
| TRONCONE     | [Genetic characterization and implications for conservation of the last autochthonous Mouflon population in Europe](https://drive.proton.me/urls/SW4YPN2ZGC#RWYgHuXfrvK4)   |
| GARCIA       | [The critically endangered vaquita is not doomed to extinction by inbreeding depression](https://drive.proton.me/urls/FJ5FMEQ8EC#QhbaqVfIyFkE)    |
| SPERA        | [Accelerated modern human-induced species losses entering the sixth mass extinction](https://drive.proton.me/urls/TQTJYX0CFR#vp0NSA7IbAva)     |
| CACCIUNI     | [Island differences in population size structure and catch per unit effort and their conservation implications for Komodo dragons](https://drive.proton.me/urls/A4H4P4BPQ4#qyJ15T7yUTeu)  |
| TOTI         | [Synergies among extinction drivers under global change](https://drive.proton.me/urls/HZ2HRWEMXR#IFj88GjFUk78)    |
| PALMERI      | [Herbarium specimens reveal the footprint of climate change on flowering trends across North America](https://drive.proton.me/urls/A8Z10R82RR#LFqcygcJtOjj)  |
| BONVENTRE    | [What is conservation Science?](https://drive.proton.me/urls/9NB7Y2T0T0#txxxIMgzHPIo)  |
